\chapter{Product information}
%Reducing the spacing from the title
\vspace{-6em}


\section{Identification}
Greenhouse is a tool that allows you to grow different plants in an efficient
way. The software allows you to monitor the different data acquisition
sensorsHeloo world on the screen.\newline


\begin{table}
\begin{center}
\label{tab:Sensors}
\begin{tabular}{| m{3cm} | m{4cm} |}
\hline
\textbf{Sensor name} & \textbf{Sensor id} \\ \hline 
Temperature & TemperatureSensorXX \\ \hline 
Humidity & HumiditySensorXX \\ \hline 
Light & HumiditySensorXX \\ \hline 
Motion & MotionSensorXX \\ 
\hline 
\end{tabular}
\end{center}
\end{table}
\begin{table}
\begin{center}
\label{tab:Sensors}
\begin{tabular}{| m{4cm} | m{4cm} |}
\hline
\textbf{Other Parts} & \textbf{ID} \\ \hline 
Security Camera & SecurityCameraXX \\ \hline 
\textbf{\emph{\glspl{EC-Meter}}} & ECMeterXX \\ \hline 
\textbf{\emph{\glspl{Ph-Meter}}} & PhMeterXX \\ \hline 
Computer & ComputerXX \\ \hline
Hard-disk & HardiskXX \\ 
\hline 
\end{tabular}
\end{center}
\end{table}

The computer runs the operating system Windows 10 Pro edition on the current
version 1703. An mouse and keyboard and a display of 24 inches are also
connected to the computer. Keyboard and mouse via cable USB and the display via
\textbf{\emph{\glspl{VGA}}}. \newline
The storage for the different datas are stored on three different hard-drives of
the company Seagate Barracuda. Two hard-drive of 512 gb for the digital storage
of the amount of crops and one for sensors data. The third one is for the video
recording of the size of 1 tb. The hard-drives are connected to the mainboard of
the computer with a Sata 3 cable for the communication. The Model Number is
ST100DM010.\newline
Inside the greenhouse:\newline
Two temperature sensors are set up in each room. Monnit Wi-Fi Temperature
Sensors which telecommunicate over wifi. It takes Batteries as energy
source. In addition the item number is MN-2-WF-TS-ST.\newline
The humidity sensor are also placed inside the big pots every square meter one. 
The Wemos Higrow ESP32 is used here to measure the humidity in the soil. The
telecommunication is over wifi and Batteries are used as power source.\newline
The light sensors are also inside the greenhouse every square meter one.\newline
The motion sensors are positioned on every corner of each room. The supported
motion sensor is the Philips Hue Motion sensor which power Source are batteries
and detects a person on a range of 5 meter. The motion sensors are connected via
wireless,in addition the motion detection range is 100 degrees. The product
number is 464602.\newline
The security camera is inside the greenhouse one in each room and on the roof.
The camera is from SV3C it can record up to 15 fps on resolution of 2592x1944
and it is waterproofed. The view angle is 80 degrees an and the connection of
the ethernet is wired. The support of video compression H.265 is also
possible.\newline
The EC-Meter is positioned inside the water tank.\newline
The ph meter is positioned inside the soil to read ph scale of the soil where
the plants are and to check the ph scale inside the water tank.\newline



\section{Copyright}
All content on the website including but not limited to  the logo of the
greenhouse the design  and the functions of the software are copyright.
Copyright © 2017 by Greenhouse All Rights Reserved. protected.

\section{Trademark notices}
The Greenhouse logo, name and software design are part of the Greenhouse
trademark. It is strictly prohibited to use anything that could be mistaken for
a Greenhouse product. Anything that influences the income of greenhouse
negatively or impacts the name of Greenhouse in a bad way. Artwork ,designs and
imagery are trademarks or copyrighted material of the Greenhouse.


\section{Restrictions}
All rights reserved. The software is licensed to the client, no part of this
software or its documentation shall be reproduced, redistributed in any from,
including taking pictures, screenshots, recording and any other electroni
methods  without the EXCLUSIVE permission from Greenhouse. The only exception is
in the case of a review of the software in a non commercial way or in the case
of educational use, it is allowed to share the experience of the project and to
criticize it.  In case of a request for a permission contact the support office
of the greenhouse at support@greenhouse.com. This product produced by MBSA Co.
allows you to operate a SPCG. The goal of this products use is to maximize crop harvest and to maintain a SPCG. The product is not meant for other uses than gardening otherwise all warranty and support will be canceled and we will not take any responsibilities towards the product.

The Software will always be our intellectual property. You are not allowed to
sell nor to copy and sell the product (including software and hardware). This is
a standalone system drafted by MBSA Co..

\section{Warranties}
Greenhouse has a for 30 days return policy. The software is covered under
warranty for one year. The warranty covers all the functionality of the software
that it executes the different actions appropriately.
Every hardware warranty will be claimed by the company who produced them.  See
the table below for the warranties of the different items.

\begin{table}
\begin{center}
\label{tab:Warrenties}
\begin{tabular}{| m{4cm} | m{4cm} | m{4cm} |}
\hline
\textbf{Manufractuer} & \textbf{Name} & \textbf{Warrentie} \\ \hline 
Seagate Barracuda & Hard-Disk & 2 Years \\ \hline 
Philps Hue & Motion Sensor & 2 Years \\ \hline 
SV3C & Security Camera & 2 Years \\ \hline 
Wemos Higrow ESP32 & Humidity Sensor & 180 Days \\ \hline
Monnit Wi-Fi & Temperature Sensor & 1 Year \\ \hline
??? & Ph-Meter & ? Year \\ \hline
??? & Ec-Meter & ? Year \\ 
\hline 
\end{tabular}
\end{center}
\end{table}


\section{Contractual obligations}
The client can only use the software for one specific project or enterprise. The
software must be installed by Greenhouse certified technicians. If the client
encounters any problems with the software Greenhouse will provide support from
certified technicians. The client is not allowed to seek support from any third
party. The computer provided is only intended for use with the software provided
by Greenhouse. The client is not allowed to install any other software or use
the computer for any other purpose. In case there is a faulty sensors the client
has to contact Greenhouse to either outright replace the sensors or to give
instructions to the client on how to repair the sensor.

\section{Disclaimers}
A refund for the software is only possible in the first 30 days after receiving
the software. Greenhouse is not responsible for any damages that occur during
unspecified use of our software. In addition Greenhouse is not responsible of
any hardware failure nor is Greenhouse responsible for any data lost in that
event, we will redirect you to the company which produced the hardware to
request warranties. Also in a case of software failure we can not be hold
responsible if any plants get harmed. Greenhouse is not responsible for any
damage done by third parties who gained unauthorized access to the software or
the webpage. Greenhouse is not responsible for any bodily or psychological harm
caused by unspecified use of the software. In case that the client modifies the
software himself the warranty for the software will be null and void. In case of
damage during a repair on a sensors Greenhouse is not responsible if the clients
technician failed to fully comply with our instructions.

\section{Contact}
Greenhouse\newline
1234 Resistance avenue\newline
Bascharage L - 4942\newline
www.greenhouse.lu\newline
It is possible to contact us via email: support@greenhouse.com or via phone: 1-800-GREENHOUSE 
\\*